The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-08 main.tex
edits to the introduction

\section{Introduction} \label{sec:intro}
All modern astronomical research makes use of software in some way.
Astronomy as a field has thus long supported the development of software tools
for astronomical tasks, such as scripts that enable individual scientific
research, software packages for small collaborations, and data reduction
pipelines for survey operations.
Some software packages are or were supported by large institutions and are
intended for a wide range of users.
These packages therefore typically provide some level of documentation and user
support or training.
Other packages are developed by individual researchers or research groups and
are then typically used by smaller groups for more domain-specific purposes.
For both packages meant for wider distribution and for scripts specific to
particular research projects, a library that addresses common astronomical tasks
simplifies the software development process.
The users of such a library then also benefit from a community and ecosystem
built around a shared foundation.
The \astropy project has grown to become this community for \python astronomy
software, and the \astropypkg core package a feature-rich \python library.

The development of the \astropypkg core package began as a largely
community-driven effort to standardize core functionality for astronomical
software in \python.
In this way, its genesis differs from but builds upon many substantial and
former astronomical software development efforts that were commissioned or
initiated through large institutional support, such as IRAF \citep[developed
at NOAO;][]{IRAF}, MIDAS \citep[developed at ESO;][]{MIDAS}, or Starlink
\citep[originally developed by a consortium of UK institutions and now
maintained by the East Asian Observatory;][]{starlink1982,starlink2013}.
More recently, community-driven efforts have seen significant success in the astronomical sciences (e.g., \citealt{yt}).

\python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
programming language that is available under a permissive open source software license free of
charge for all major operating systems. The programming language has become especially popular
in the quantitative sciences, where researchers must simultaneously produce research, perform
data analysis, and develop software. A large part of this success owes itself to the vibrant
community of developers and a continuously-growing ecosystem of tools, web services, and stable
well-developed packages that enable easier collaboration on software development, easier
writing and sharing of software documentation, and continuous testing and validation of
software. While dedicated libraries provide support for array representation and
arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
computing \citep[\package{scipy};][]{scipy}, and publication-quality plotting
\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high-quality and easy-to-use
packages are available, which can help with tasks that are not specific to astronomy but
might be performed in the course of astronomical research, e.g., interfacing with
databases, or statistical inferences.
More recently, the development and mainstream adoption of package managers such
as Anaconda\footnote{\url{https://anaconda.org/}} has significantly streamlined
the installation process for many libraries, lowering many barriers to entry.

@@

We start by describing the way the \astropy project functions and is organized
in \sectionname~\ref{sec:org}. We then describe the main software efforts
developed by the \astropy project itself: a core package called \astropypkg
(\sectionname~\ref{sec:core}) and several separate packages that help maintain
the infrastructure for, e.g., testing and documentation
(\sectionname~\ref{sec:infrastructure}). We end with a short vision for
the future of \astropy and astronomical software in general in
\sectionname~\ref{sec:future}.

>>>>

\section{Introduction} \label{sec:intro}
All modern astronomical research makes use of software in some way.
Astronomy as a field has thus long supported the development of software tools
for astronomical tasks, such as scripts that enable individual scientific
research, software packages for small collaborations, and data reduction
pipelines for survey operations.
Some software packages are, or were, supported by large institutions and are
intended for a wide range of users.
These packages therefore typically provide some level of documentation and user
support or training.
Other packages are developed by individual researchers or research groups and
are then typically used by smaller groups for more domain-specific purposes.
For both packages meant for wider distribution and for scripts specific to
particular research projects, a library that addresses common astronomical tasks
simplifies the software development process.
The users of such a library then also benefit from a community and ecosystem
built around a shared foundation.
The \astropy project has grown to become this community for \python astronomy
software, and the \astropypkg core package is a feature-rich \python library.

The development of the \astropypkg core package began as a largely
community-driven effort to standardize core functionality for astronomical
software in \python.
In this way, its genesis differs from, but builds upon, many substantial and
former astronomical software development efforts that were commissioned or
initiated through large institutional support, such as IRAF \citep[developed
at NOAO;][]{IRAF}, MIDAS \citep[developed at ESO;][]{MIDAS}, or Starlink
\citep[originally developed by a consortium of UK institutions and now
maintained by the East Asian Observatory;][]{starlink1982,starlink2013}.
More recently, community-driven efforts have seen significant success in the astronomical sciences (e.g., \citealt{yt}).

\python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
programming language that is available under a permissive open source software license and is free of
charge for all major operating systems. The programming language has become especially popular
in the quantitative sciences, where researchers must simultaneously produce research, perform
data analysis, and develop software. A large part of this success owes itself to the vibrant
community of developers and a continuously-growing ecosystem of tools, web services, and stable
well-developed packages that enable easier collaboration on software development, easier
writing and sharing of software documentation, and continuous testing and validation of
software. While dedicated libraries provide support for array representation and
arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
computing \citep[\package{scipy};][]{scipy}, and publication-quality plotting
\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high-quality and easy-to-use
packages are available, which can help with tasks that are not specific to astronomy but
might be performed in the course of astronomical research, e.g., interfacing with
databases, or statistical inferences.
More recently, the development and mainstream adoption of package managers such
as Anaconda\footnote{\url{https://anaconda.org/}} has significantly streamlined
the installation process for many libraries, lowering the barriers to entry.

@@

We start by describing the way the \astropy project functions and is organized
in \sectionname~\ref{sec:org}. We then describe the main software efforts
developed by the \astropy project itself: a core package called \astropypkg
(\sectionname~\ref{sec:core}) and several separate packages that help maintain
the infrastructure for testing and documentation
(\sectionname~\ref{sec:infrastructure}). We end with a short vision for
the future of \astropy and astronomical software in general in
\sectionname~\ref{sec:future}.
